---
title: "Binary Data Regression Models for Bank Customer Attrition"
---


```{r}
br.data = read.csv("Bank_Rentention_Data.csv")
```
We estimate the following binary data regression model using the R function glm( ). 

Churn ~ B0 + B1×Agei + B2×Incomei+B3×HomeVali + B4×Tenurei 
                +B5×DirectDepositi + B6×LoanIndi +B7×Disti + B8×MktSharei
                                                   
We use both of the logit (for logistic regression) and probit (for probit regression) link functions of the binomial family.

```{r}
br.glm1=glm(Churn~Age+Income+HomeVal+Tenure+DirectDeposit+Loan+Dist+MktShare, data=br.data,family = binomial(link="logit"))
summary(br.glm1)
br.glm2=glm(Churn~Age+Income+HomeVal+Tenure+DirectDeposit+Loan+Dist+MktShare, data=br.data,family = binomial(link="probit"))
summary(br.glm2)
```
In both models, B6 and B8 are not statistically significant, but B1, B2, B3, B4, B5 and B7 are. 
B1 : If age increases, the probability of churn will decrease.
B2 : If income increases, the probability of churn will also increase.
B3  : If homeval increases, the probability of churn will decrease.
B4 : If tenure increases, the probability of churn will decrease.
B5: If directdeposit increases, the probability of churn will decrease.
B7: If dist increases, the probability of churn will also increase.
```{r}
AIC(br.glm1)
AIC(br.glm2)
BIC(br.glm1)
BIC(br.glm2)
```
According to this, the probit model is slightly better.

Next we will use a random effect grouped by TractID in the logistic regression. 
We use the function glmer( ) in the "lme4" package in R to fit 

Churn ~ B0 + B1×Age + B2×Income +B3×HomeVal + B4×Tenure
                    +B5×DirectDeposit + B6×LoanInd +B7×Dist + B8×MktShare
                                                                                            
where B0 is the random effect for the p-th census tract (TractID). 
```{r}
br.glm3=glmer(Churn~Age+Income+HomeVal+Tenure+DirectDeposit+Loan+Dist+MktShare+(1|TractID), data=br.data,family = binomial,glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=100000)))
summary(br.glm3)
```
```{r}
AIC(br.glm3)
BIC(br.glm3)
```
Similar to the above, B6 and B8 are not statistically significant unlike B1, B2, B3, B4, B5 and B7. 

Based on AIC and BIC, this model does not fit the dataset as well as the models in previous question.


Continuing on with the model above, we use the MCMCpack function MCMChlogit() to estimate the same parameters with Bayesian estimation. Because the model only has a random intercept, we specify random=~1 and r=2, R=1 in the MCMChlogit() function. We set burnin=10000, mcmc=20000 and thin=20.
```{r}
a= MCMChlogit(Chrun~Age+Income+HomeVal+Tenure+DirectDeposit+Loan+Dist+MktShare, random=~1,group = "TractID", data=mv.data, burnin = 10000, mcmc = 20000, thin = 20,r = 2,R=diag(1))
summary(a$mcmc[,1:9])
```
We can see how the fixed effects are significant at the 5% level.

```{r}
plot(a$mcmc[,6])
plot(a$mcmc[,3])
```



